---
title: "Coronavirus Beliefs"
author: "Ruiyu Li"
date: "2026-03-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

options(scipen = 999)

d_coronavirus <- read.csv("../data/life-under-lockdown-wave2-extract.csv")
```

#Hypothesis
H1 Gender is associated with number of conspiracy beliefs
H2 Age is associated with number of conspiracy beliefs regarding coronavirus
H3 Reliance on facebook for information about coronavirus is associated with number of conspiracy beliefs regarding coronavirus

#Analysis 1
```{r}
d_coronavirus %>%
  group_by(gender) %>%
  summarise(
    n = n(),
    Mdn = median(beliefs, na.rm = TRUE),
    M = mean(beliefs),
    SD = sd(beliefs)
  )
```


```{r}
d_coronavirus %>%
  filter(gender != "In another way") %>%
  t.test(
    beliefs ~ gender,
    data = .
  #把前面 pipe 传过来的那个筛选后的数据，作为 data 使用。
  )
```

#Findings 1
In the sample, males held more conspiracy beliefs regarding coronavirus than females, but this was not statistically significant, t(494.31) = -1.201, p = .230.


#Hypothesis 2
```{r}
d_coronavirus %>%
  ggplot(
    aes(
      x = age,
      y = beliefs
    )
  ) + 
  geom_jitter()
```


```{r}
d_coronavirus %>%
cor.test(
    ~ beliefs + age,
    data = .
)
```

#Findings 2
Age is negatively associated with number of conspiracy belifes about coronavirus, r(498) = .24, p < .001.


#Hypothesis 3
```{r}
knowledge_level <- c(
  "Nothing at all", 
  "Not very much", 
  "A fair amount", 
  "A great deal")

d_coronavirus <- d_coronavirus %>%
  mutate(
    know_facebook = know_facebook %>%
      ordered(
        levels = knowledge_level
      )
  )

d_coronavirus %>%
  ggplot(
    aes(
      x = know_facebook,
      y = beliefs
    )
  ) + 
  geom_violin()
```

```{r}
d_coronavirus <- d_coronavirus %>% 
  mutate(
    know_facebook_coded = know_facebook %>% 
      as.numeric()
  )

d_coronavirus %>%
 cor.test(
    ~ beliefs + know_facebook_coded,
    data = .,
    method = "spearman"
)
```
#Findings 3
Reliance on Facebook for knowledge of coronavirus is positively associated with number of conspiracy beliefs about coronavirus, rs(498) = .23, p < .001.