---
title: "Coronavirus Beliefs"
author: "Ruiyu Li"
date: "2026-03-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readr)
library(ggplot2)

options(scipen = 999)

d_coronavirus <- read.csv("../data/life-under-lockdown-wave2-extract.csv")
```

#Hypothesis
H1 Gender is associated with number of conspiracy beliefs
H2 Age is associated with number of conspiracy beliefs regarding coronavirus

#Analysis
```{r}
d_coronavirus %>%
  group_by(gender) %>%
  summarise(
    n = n(),
    Mdn = median(beliefs, na.rm = TRUE),
    M = mean(beliefs),
    SD = sd(beliefs)
  )
```


```{r}
d_coronavirus %>%
  filter(gender != "In another way") %>%
  t.test(
    beliefs ~ gender,
    data = .
  #把前面 pipe 传过来的那个筛选后的数据，作为 data 使用。
  )
```

#Findings
In the sample, males held more conspiracy beliefs regarding coronavirus than females, but this was not statistically significant, t(494.31) = -1.201, p = .230.


#Hypothesis 2
```{r}
d_coronavirus %>%
  ggplot(
    aes(
      x = age,
      y = beliefs
    )
  ) + 
  geom_jitter()
```


```{r}
d_coronavirus %>%
cor.test(
    ~ beliefs + age,
    data = .
)
```

#Findings
Age is negatively associated with number of conspiracy belifes about coronavirus, r(498) = .24, p < .001.